---
title: "transformations.qmd_01"
format: html
editor: visual
author: Elad Benjo
---

# Intro

this notebooks describes the suggested transformations pipeline:

RAW -\> Price Adjustments (FX and CPI) -\> Seasonality -\> Final Transformations

# Utilities

## Packages

```{r}
# Load every session
library(dplyr)
library(tidyr)
library(ggplot2)
library(zoo)
library(readxl)
library(purrr)
library(tseries)
library(forecast)
library(seasonal)
library(lubridate)
```

## Scripts

### Save Tables

```{r}
save_list_to_excel <- function(lst, file_path = "output.xlsx") {
  # lst: a named list of data.frames
  # file_path: output Excel file path
  
  # Require openxlsx
  if (!requireNamespace("openxlsx", quietly = TRUE)) {
    stop("Package 'openxlsx' is required but not installed.")
  }
  
  # Create workbook
  wb <- openxlsx::createWorkbook()
  
  # Loop through list elements and add worksheets
  for (sheet_name in names(lst)) {
    
    # Add worksheet
    openxlsx::addWorksheet(wb, sheet_name)
    
    # Write the data frame
    openxlsx::writeData(wb,
                        sheet = sheet_name,
                        x = lst[[sheet_name]])
  }
  
  # Save workbook
  openxlsx::saveWorkbook(wb,
                         file = file_path,
                         overwrite = TRUE)
  
  message("Saved Excel file: ", file_path)
}

```

# Stationary:

in this notebook we will take our daily, monthly and quarterly tables, examine the stationarity and seasonality of each series, apply the right transformations and re-evaluate.

## Import data sets:

```{r}
path <- "C:/Users/eladb/OneDrive/Desktop/University/2025 B/Nowcasting/Seminar/data/raw/nowcasting_data_raw.xlsx"
```

```{r}
sheets <- excel_sheets(path)
```

```{r}
blocks_raw <- sheets %>% 
  set_names() %>% 
  map(~ read_excel(path, sheet = .x))

blocks_real <- sheets %>% 
  set_names() %>% 
  map(~ read_excel(path, sheet = .x))
```

```{r}
blocks_raw <- map(blocks_raw, ~ {
  df <- .x
  df$Date <- as.Date(df$Date)
  df
})

blocks_real <- map(blocks_raw, ~ {
  df <- .x
  df$Date <- as.Date(df$Date)
  df
})
```

## Price Adjustment

in this first step we are addressing variables that are in nominal form or in foreign currency. generally all tax data is adjusted with CPI, OIL and FX reserves are treated both with CPI and USD/ILS.

### Create Function

```{r}
adjust_block_for_cpi <- function(block_df, cpi_df, cols = "all") {
  # join by date
  df <- block_df %>%
    dplyr::left_join(cpi_df %>% dplyr::select(Date, CPI), by = "Date")
  
  # CPI test for NA's
  if (any(is.na(df$CPI))) {
    warning("There are NA values in CPI after merging. Check date alignment.")
  }
  
  # select cols
  if (identical(cols, "all")) {
    cols_to_adjust <- setdiff(names(df), c("Date", "CPI"))
  } else {
    cols_to_adjust <- cols
  }
  
  # adjust for real values
  for (col in cols_to_adjust) {
    # skip non-exisitng cols
    if (!col %in% names(df)) {
      warning(paste("Column", col, "not found in block. Skipping."))
      next
    }
    
    # override with real val
    df[[col]] <- df[[col]] / (df$CPI / 100)
  }
  
    # remove CPI
    df <- df %>% dplyr::select(-CPI)
  
  return(df)
}

```

### Apply

bellow I'm using the function on all TAX blocks, as well as the taxes in Real estate block, then last Oil and FX reserves.

```{r}
blocks_real$personal_labor_income_taxes <-
  adjust_block_for_cpi(blocks_raw$personal_labor_income_taxes,
                       blocks_raw$adjusters)
```

```{r}
blocks_real$corporate_business_tax <-
  adjust_block_for_cpi(blocks_raw$corporate_business_tax,
                       blocks_raw$adjusters)
```

```{r}
blocks_real$consumption_tax <-
  adjust_block_for_cpi(blocks_raw$consumption_tax,
                       blocks_raw$adjusters)
```

```{r}
blocks_real$import_trade_tax <-
  adjust_block_for_cpi(blocks_raw$import_trade_tax,
                       blocks_raw$adjusters)
```

```{r}
blocks_real$real_estate <-
  adjust_block_for_cpi(blocks_raw$real_estate,
                       blocks_raw$adjusters,
                       cols = c("Real estate taxation",
                                "Property tax",
                                "praise tax",
                                "Real estate purchase tax",
                                "praise tax returns",
                                "purchase returns"))
```

adjusting oil to USD/ILS and CPI

```{r}
blocks_real$real_activity$Oil <- blocks_raw$real_activity$Oil * blocks_raw$FX_liqudity$Dollar
```

```{r}
blocks_real$real_activity <-
  adjust_block_for_cpi(blocks_real$real_activity,
                       blocks_real$adjusters,
                       cols = "Oil")
```

```{r}
blocks_real$FX_liqudity$`Foreign exchange reserves (millions of dollars)` <- blocks_raw$FX_liqudity$`Foreign exchange reserves (millions of dollars)` * blocks_raw$FX_liqudity$Dollar
```

```{r}
blocks_real$FX_liqudity <-
  adjust_block_for_cpi(blocks_real$FX_liqudity,
                       blocks_real$adjusters,
                       cols = "Foreign exchange reserves (millions of dollars)")
```

quick peek and validation

```{r}
head(blocks_real$FX_liqudity$`Foreign exchange reserves (millions of dollars)`)
```

```{r}
head(blocks_raw$FX_liqudity$`Foreign exchange reserves (millions of dollars)`)
```

### Save Results

since I didn't automate this yet, manually tracking meta data:

1.  all taxes blocks adjusted by CPI (refer to specifics in Real Estate block)
2.  Oil and FX reserves are adjusted USD and CPI

```{r}
save_list_to_excel(blocks_real, "blocks_real.xlsx")
```

## Seasonality

in this part we are using MoFi script to treat Israeli seasonality in the data

### Create Function

load files

```{r}
td <- read_csv("C:/Users/eladb/OneDrive/Desktop/University/2025 B/Nowcasting/Seasonality by Yotam/SA_CODE/Data/td_var.csv")
td_ts <- ts(
  td[, -1],
  start = c(year(min(td$date)), month(min(td$date))),
  frequency = 12
)

preadj <- read_excel("C:/Users/eladb/OneDrive/Desktop/University/2025 B/Nowcasting/Seasonality by Yotam/SA_CODE/Data/hol_preadj.xlsx") %>%
  mutate(date = as.Date(date))

hag_ts <- ts(
  preadj[, -1],
  start = c(year(min(preadj$date)), month(min(preadj$date))),
  frequency = 12
)
```

```{r}
seasonal_adjust_block <- function(block_df,
                                  columns = "all",
                                  hag_ts,
                                  td_ts,
                                  x11 = TRUE,
                                  outlier_types = "ao") {
  
  # Ensure 'Date' column exists
  if (!"Date" %in% names(block_df)) {
    stop("The block must contain a 'Date' column.")
  }
  
  # Select variables to process
  if (identical(columns, "all")) {
    vars <- setdiff(names(block_df), "Date")
  } else {
    vars <- columns
  }
  
  # Output containers
  info_list <- list()
  df_out <- block_df
  
  # Loop through variables
  for (v in vars) {
    message("Running SA on variable: ", v)
    
    x <- df_out[[v]]
    
    # Skip if all NA
    if (all(is.na(x))) {
      info_list[[v]] <- data.frame(
        variable = v,
        status = "Skipped - all NA",
        transform = NA,
        arima = NA,
        outliers = NA,
        stringsAsFactors = FALSE
      )
      next
    }
    
    # Identify leading NA region
    first_non_na <- min(which(!is.na(x)))
    last_non_na  <- max(which(!is.na(x)))
    segment <- x[first_non_na:last_non_na]
    
    # Skip if NA inside the segment (not allowed in X-13)
    if (any(is.na(segment))) {
      info_list[[v]] <- data.frame(
        variable = v,
        status = "Skipped - NA inside the series",
        transform = NA,
        arima = NA,
        outliers = NA,
        stringsAsFactors = FALSE
      )
      next
    }
    
    # Create TS object using full date range
    y <- ts(
      segment,
      start = c(year(df_out$Date[first_non_na]),
                month(df_out$Date[first_non_na])),
      frequency = 12
    )
    
    # Run X-13
    fit <- tryCatch({
      if (x11) {
        seas(
          y,
          x11 = "",
          outlier.types = outlier_types,
          transform.function = "auto",
          xreg = cbind(hag_ts, td_ts),
          regression.usertype = rep("holiday", ncol(hag_ts))
        )
      } else {
        seas(
          y,
          outlier.types = outlier_types,
          transform.function = "auto",
          xreg = cbind(hag_ts, td_ts),
          regression.usertype = rep("holiday", ncol(hag_ts))
        )
      }
    }, error = function(e) {
      info_list[[v]] <<- data.frame(
        variable = v,
        status = paste("SA failed:", e$message),
        transform = NA,
        arima = NA,
        outliers = NA,
        stringsAsFactors = FALSE
      )
      return(NULL)
    })
    
    if (is.null(fit)) next
    
    # Extract metadata
    trans_used <- tryCatch(as.character(fit$series$transfunc)[1], error = function(e) NA)
    arima_used <- tryCatch(paste(as.character(fit$est$arima), collapse = "; "), error = function(e) NA)
    outliers_used <- tryCatch(paste(as.character(fit$outlier$Type), collapse = ", "), error = function(e) NA)
    
    info_list[[v]] <- data.frame(
      variable = v,
      status = "OK",
      transform = trans_used,
      arima = arima_used,
      outliers = outliers_used,
      stringsAsFactors = FALSE
    )
    
    # --- Corrected assignment with leading NA preserved ---
    adj <- as.numeric(predict(fit))
    
    # Fill inside the original vector
    result_vec <- x
    result_vec[first_non_na:last_non_na] <- adj
    
    df_out[[v]] <- result_vec
  }
  
  return(list(
    data = df_out,
    info = dplyr::bind_rows(info_list)
  ))
}

```

### Apply

duplicate "blocks_real" into a new variable

```{r}
blocks_sa <- blocks_real
```

create a list to save transformation meta-data into

```{r}
sa_info <- list()
```

in this chunk below you run the SA script, results are then stored in "out" and written to both "blocks_sa" and meta data. adjust with your desired block and save path.

```{r}
out <- seasonal_adjust_block(
    blocks_real$real_estate, # choose your block
    columns = c("Real estate taxation",
                "Property tax",
                "praise tax",
                "Real estate purchase tax",
                "praise tax returns",
                "purchase returns"),
    hag_ts = hag_ts,
    td_ts = td_ts
)

blocks_sa$real_estate <- out$data # override with the SA data
sa_info$real_estate   <- out$info # save trans meta-data

```

### Save Results

save seasonal transformation meta-data

```{r}
write_sa_info <- function(sa_info, file_path = "sa_info.xlsx") {
  wb <- createWorkbook()
  
  for (bn in names(sa_info)) {
    addWorksheet(wb, bn)
    writeData(wb, bn, sa_info[[bn]])
  }
  
  saveWorkbook(wb, file = file_path, overwrite = TRUE)
}
```

```{r}
write_sa_info(sa_info, "SA_results_01.xlsx")
```

```{r}
save_list_to_excel(blocks_sa, "blocks_sa_01.xlsx")
```

## Transformations

### Tests

kpss and adf tests for stationary series

#### Create Function

```{r}
test_transform <- function(x, freq = 12, alpha = 0.05) {
  
  x_clean <- na.omit(x)
  if (length(x_clean) < 24) return("too_short")
  
  # 1. Seasonality check with STL
  seas_strength <- NA
  has_seasonality <- FALSE
  if (freq > 1 && length(x_clean) > freq * 2) {
    stl_obj <- tryCatch(stl(ts(x_clean, frequency = freq), s.window = "periodic"), error = function(e) NULL)
    if (!is.null(stl_obj)) {
      seas <- stl_obj$time.series[, "seasonal"]
      resid <- stl_obj$time.series[, "remainder"]
      seas_strength <- max(0, 1 - var(resid) / var(seas + resid))
      has_seasonality <- seas_strength > 0.3
    }
  }
  
  # 2. ADF test
  adf_p <- tryCatch(adf.test(x_clean)$p.value, error = function(e) NA)
  
  # 3. KPSS test
  kpss_p <- tryCatch(kpss.test(x_clean)$p.value, error = function(e) NA)
  
  # 4. LOG possible?
  positive_only <- all(x_clean > 0)
  
  # 5. Logic
  adf_stationary <- !is.na(adf_p)  && adf_p < alpha
  kpss_stationary <- !is.na(kpss_p) && kpss_p > alpha
  
  # Base decision
  if (adf_stationary && kpss_stationary) {
    base <- "none"
  } else if (!adf_stationary && !kpss_stationary) {
    base <- "diff"
  } else if (adf_stationary && !kpss_stationary) {
    base <- "detrend"
  } else {
    base <- "diff"
  }
  
  # Prefer LOGDIFF if possible
  if (base == "diff" && positive_only) base <- "logdiff"
  
  # Add seasonality
  if (has_seasonality) {
    if (base == "none") {
      base <- "seasonal_diff"
    } else {
      base <- paste0(base, "+seasonal_diff")
    }
  }
  
  return(base)
}
```

#### Apply

apply on each block and save the results in a list like variable, later we will apply transformations with the recommended ones we got there.

```{r}
block <- blocks_sa$personal_labor_income_taxes
trans_01 <- sapply(block %>% dplyr::select(-Date), test_transform)
```

```{r}
block <- blocks_sa$corporate_business_tax
trans_02 <- sapply(block %>% dplyr::select(-Date), test_transform)
```

```{r}
block <- blocks_sa$consumption_tax
trans_03 <- sapply(block %>% dplyr::select(-Date), test_transform)
```

```{r}
block <- blocks_sa$import_trade_tax
trans_04 <- sapply(block %>% dplyr::select(-Date), test_transform)
```

```{r}
block <- blocks_sa$real_estate
trans_05 <- sapply(block %>% dplyr::select(-Date), test_transform)
```

```{r}
block <- blocks_sa$real_activity
trans_06 <- sapply(block %>% dplyr::select(-Date), test_transform)
```

```{r}
block <- blocks_sa$labor
trans_07 <- sapply(block %>% dplyr::select(-Date), test_transform)
```

```{r}
block <- blocks_sa$capital_markets
trans_08 <- sapply(block %>% dplyr::select(-Date), test_transform)
```

```{r}
block <- blocks_sa$FX_liqudity
trans_09 <- sapply(block %>% dplyr::select(-Date), test_transform)
```

### Transform

after testing for required transformation for each variable, in this section we can go ahead and start applying, test again at the end. note that for some variables that "detrend" was recommended I ended up applying "diff" or "logdiff" instead for cases where detrend didn't work, final transformations is stored in the report.

#### Create Function

```{r}
transform_block <- function(block_df, codes_vector, freq = 12) {
  
  block_df <- as.data.frame(block_df)
  
  if (!"Date" %in% names(block_df)) stop("Date column missing.")
  
  vars <- setdiff(names(block_df), "Date")
  if (length(vars) != length(codes_vector)) stop("codes length mismatch.")
  
  out_df <- block_df
  info_list <- list()
  
  for (i in seq_along(vars)) {
    
    varname <- vars[i]
    code <- codes_vector[i]
    x <- out_df[[varname]]
    n <- length(x)
    
    # always initialize full-length result
    result <- rep(NA, n)
    
    transformed <- tryCatch({
      
      if (code == 0) {
        result <- x
        result
        
      } else if (code == 1) {
        result <- log(x)
        result
        
      } else if (code == 2) {
        result[2:n] <- diff(x)
        result
        
      } else if (code == 3) {
        lx <- log(x)
        result[2:n] <- diff(lx)
        result
        
      } else if (code == 4) {
        if (n > freq) result[(freq+1):n] <- x[(freq+1):n] - x[1:(n-freq)]
        result
        
      } else if (code == 5) {
        if (n > freq) {
          sd <- x[(freq+1):n] - x[1:(n-freq)]
          result[(freq+1):n] <- log(sd)
        }
        result
        
      } else if (code == 6) {
        if (n > freq+1) {
          sd <- x[(freq+1):n] - x[1:(n-freq)]
          result[(freq+2):n] <- diff(sd)
        }
        result
        
      } else if (code == 7) {
        if (n > freq+1) {
          lx <- log(x)
          ld <- diff(lx)
          result[(freq+2):n] <- ld[(freq+1):(n-1)] - ld[1:(n-freq-1)]
        }
        result
        
      } else if (code == 8) {
        # Identify non-NA segment
        first_non_na <- min(which(!is.na(x)))
        last_non_na  <- max(which(!is.na(x)))
        
        x_seg <- x[first_non_na:last_non_na]
        t_seg <- seq_len(length(x_seg))
        
        # Detrend only this segment
        detr <- residuals(lm(x_seg ~ t_seg))
        
        # Place back into full result vector
        result <- rep(NA, n)
        result[first_non_na:last_non_na] <- detr
        
        result
        
      } else {
        stop("Unknown code.")
      }
      
    }, error = function(e) {
      warning(paste("Failed", varname, ":", e$message))
      rep(NA, n)
    })
    
    # FORCE LENGTH TO MATCH
    if (length(transformed) != n) {
      tmp <- rep(NA, n)
      tmp[1:length(transformed)] <- transformed
      transformed <- tmp
    }
    
    # assign safely
    out_df[[varname]] <- transformed
    
    info_list[[varname]] <- data.frame(
      variable = varname,
      code = code,
      transformation = c(
        "none","log","diff","logdiff",
        "seasonal_diff","log_seasonal_diff",
        "diff_seasonal_diff","logdiff_seasonal_diff",
        "detrend"
      )[code + 1],
      stringsAsFactors = FALSE
    )
  }
  
  return(list(
    data = out_df,
    info = dplyr::bind_rows(info_list)
  ))
}


```

#### Apply

print the suggested transformation we stored earlier

```{r}
trans_09
```

Transformations codes:

0.  None
1.  log(x)
2.  diff(x)
3.  logdiff = diff(log(x))
4.  seasonal diff (x - lag12(x))
5.  log(seasonal diff)
6.  diff(seasonal diff)
7.  logdiff + seasonal diff
8.  detrend (remove linear trend)

in the chunks bellow results from transformation are saved into "out" then written to "blocks_transformed" and meta data is save to "transformation_info"

```{r}
block <- blocks_sa$FX_liqudity # choose your block
codes <- c(3,3,3) # transformations vector
```

```{r}
out <- transform_block(block, codes)

blocks_transformed$FX_liqudity <- out$data # adjust to your block
transformation_info$FX_liqudity <- out$info # adjust to your block

```

test for the results of the transformations, I save it to a corresponding "trans_nn_test" and plotting as needed.

```{r}
block <- blocks_transformed$FX_liqudity # choose the same block
trans_09_test <- sapply(block %>% dplyr::select(-Date), test_transform) # choose number
```

```{r}
plot.ts(blocks_transformed$FX_liqudity$`Foreign exchange reserves (millions of dollars)`)
```

### Save results

```{r}
save_transformation_info <- function(info_list, file_path = "transformation_info.xlsx") {
  # info_list: a named list where each element is a data.frame of metadata
  # file_path: output Excel file
  
  if (!requireNamespace("openxlsx", quietly = TRUE)) {
    stop("Package 'openxlsx' is required but not installed.")
  }
  
  # Create workbook
  wb <- openxlsx::createWorkbook()
  
  # Loop through list elements
  for (block_name in names(info_list)) {
    
    # Add worksheet with the block name
    openxlsx::addWorksheet(wb, block_name)
    
    # Write the info table
    openxlsx::writeData(wb, 
                        sheet = block_name, 
                        x = info_list[[block_name]])
  }
  
  # Save file
  openxlsx::saveWorkbook(wb, file = file_path, overwrite = TRUE)
  
  message("Saved: ", file_path)
}

```

```{r}
save_transformation_info(transformation_info, "TRANSFORMATION_INFO.xlsx")

```

```{r}
save_list_to_excel(blocks_transformed, "blocks_transformed.xlsx")
```

### Conclusions

1.  Consider eliminating FX_liqudiy, moving "reer" and "reserves" to the "capital_markets" block
2.  take a second look into: **FIXED ALL OF THESE RESULTS VISUALIZED**
    1.  Block: "corporate_business_tax", Var: "Goods and services" (seasonal-diff) and "excess expenses" (detrend) - both might be non-stationary after transformations
    2.  Block: "real_estate", Var: "Real estate purchase tax" (detrend)

```{r}
plot.ts(blocks_transformed$corporate_business_tax$`Goods and services`)
```

```{r}
plot.ts(blocks_transformed$corporate_business_tax$`excess expenses`)
```

```{r}
plot.ts(blocks_transformed$real_estate$`Real estate purchase tax`)
```

```{r}
plot.ts(blocks_transformed$FX_liqudity$`Foreign exchange reserves (millions of dollars)`)
```

Series to re-consider:

```{r}
plot.ts(blocks_transformed$personal_labor_income_taxes$`Total refunds from the Income Tax Department`)
```

```{r}
plot.ts(blocks_transformed$personal_labor_income_taxes$`Capital Gains Tax Refunds`)
```

```{r}
plot.ts(blocks_transformed$personal_labor_income_taxes$`Non-profit institution tax`)
```

```{r}
plot.ts(blocks_transformed$corporate_business_tax)
```

```{r}
plot.ts(blocks_transformed$corporate_business_tax$`Cancellation companies`)
```

```{r}
plot.ts(blocks_transformed$corporate_business_tax$`tax differential companies`)
```

```{r}
plot.ts(blocks_transformed$corporate_business_tax$`Cancellations Deductions`)
```

```{r}
plot.ts(blocks_transformed$corporate_business_tax$`Bonds and dividends`)
```

```{r}
plot.ts(blocks_transformed$corporate_business_tax$`Companies returns`)
```

```{r}
plot.ts(blocks_transformed$import_trade_tax$`Total import taxes`)
```

```{r}
plot.ts(blocks_transformed$real_estate$`praise tax returns`)
```

```{r}
plot.ts(blocks_transformed$real_estate$`Apartments sold at an annual rate`)
```

```{r}
plot.ts(blocks_transformed$FX_liqudity)
```

# Release Lags

right after finishing the transformations, we should also address the release lags in our data.

as it is right now, for each month, the corresponding data is sitting in the beginning of the month, for example tax collected during March 2012 is showing 03/01/2012 in our records, however in the time of nowcasting this data won't be available for us, since it is reported at the earliest by 04/01/2012.

to simplify the adjustment I am using this set of rules:

| Release Lag (from end of month) | Push             |
|---------------------------------|------------------|
| \<30                            | 1 month forward  |
| \>30                            | 2 months forward |
| \>60                            | 3 months forward |

for example:\
assuming tax data is released in a 15 days lag from EoM then instead of storing it 03/01/2012 it is now pushed forward and stored 04/01/2012.\
index data released 50 after EoM and was stored 03/01/2012 is now 05/01/2012.\
labor data released 64 days after EoM was stored 03/01/2012 is now 06/01/2012\

### Create Function

```{r}
shift_by_vector <- function(df, vec) {
  # df: data.frame where the first column is 'Date'
  # vec: numeric vector of lags, matching columns 2..n of df
  
  # Sanity check
  if (length(vec) != (ncol(df) - 1)) {
    stop("Length of vec must match number of data columns (excluding Date).")
  }
  
  df_shifted <- df
  
  # Prepare the report
  report <- data.frame(
    variable = colnames(df)[-1],
    lag_applied = vec,
    stringsAsFactors = FALSE
  )
  
  # Apply shifts
  for (i in seq_along(vec)) {
    k <- vec[i]
    var <- colnames(df)[i + 1]   # +1 to skip Date
    
    if (!is.numeric(df[[var]])) {
      warning(paste("Column", var, "is not numeric — skipped."))
      next
    }
    
    if (k > 0) {
      # Shift forward: NA at the top, drop the last k values
      df_shifted[[var]] <- c(rep(NA, k), df[[var]][1:(nrow(df) - k)])
    } else {
      # k == 0: no change
      df_shifted[[var]] <- df[[var]]
    }
  }
  
  return(list(
    data = df_shifted,
    report = report
  ))
}
```

### Apply

initiate

```{r}
blocks_shifted <- blocks_transformed
shift_report <- list()
```

run for each block

```{r}
block <- blocks_transformed$FX_liqudity # choose your block
lags <- c(1,0,1) # rep(val, n)
```

```{r}
out <- shift_by_vector(block, lags)

blocks_shifted$FX_liqudity <- out$data
shift_report$FX_liqudity <- out$report
```

### Save Results

```{r}
save_list_to_excel(blocks_shifted, "blocks_shifted.xlsx")
```

```{r}
save_transformation_info(shift_report, "shift_report.xlsx")
```
